Improving \textsl{Gaia} parallaxes with a data-driven model of the color--magnitude diagram

### 2017-02-21 paperDistance/paper.tex
dust subsection

>>>>

\subsection{Dust}

Dust corrections are non trivial for stars with poor signal to noise. Stars with poor signal to noise have a likelihood that is consistent with infinite distance and can therefore have severe dust corrections. This is most obvious in the giants, which tend to have the lowest signal to noise, and can therefore have dust corrections $\sim 1-2$ magnitudes. To apply a dust correction to the 2MASS photometry, we first generate our prior using XD on the observed, attenuated photometry. Using this raw prior we infer the distances to all the stars in our prior more precisely, increasing our signal to noise for each star and therefore minimize severe distances and their associated severe dust corrections. With more precise distance posteriors, we take the $5\%$ quantile of each distance posterior, so the closest bit of the posterior, and sample the Green et al 3D dust map at that distance. For each distance we take the median of the samples of the dust model. We apply each dust correction to our 2MASS photometry given by Equation \ref{eq:dust} where $K_{\lambda}$ = [3.626, 2.742, 3.303, 2.285, 1.698] for bands [B, V, g, r, i] respectively, taken from table (REF TABLE SFD), and $E(B-V)$ is the output of the Green et al dust models. We then regenerate our prior using the dust corrected photometry. We do not update the errors, but keep them the same as before the dust correction, which is wrong and under representing our errors but this leads again to a lighter deconvolution.

\begin{equation}
\label{eq:dust}
m_{\mathrm{band, corrected}} = m_{\mathrm{band}} - K_{\lambda} \times E(B-V)
\end{equation}
